### 2022-03-15 paper/localpsf.tex
add impulse response batches figure

We assume:
\begin{itemize}
	\item The supports of the impulse responses $\impulseresponse_x$ are contained (or approximately contained) in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all (or nearly all) $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{itemize}
Because of these assumptions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop$ to a small number of polynomial functions. We use the support estimates to compute scattered impulse responses in batches. This allows us to recover $\phi_{x_i}$'s for a large number of points $x_i$ using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme.

@@

>>>>

We assume:
\begin{itemize}
	\item The supports of the impulse responses $\impulseresponse_x$ are contained (or approximately contained) in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all (or nearly all) $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{itemize}
Because of these assumptions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop$ to a small number of polynomial functions. We use the support estimates to compute scattered impulse responses in batches. This batching allows us to recover many impulse responses using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme.

@@

\begin{figure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch1.png}
%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch12.png}
		%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch19.png}
%		\caption{Non-symmetric}
	\end{subfigure}
	\caption{Batches, $\eta_b$, of normalized impulse responses, $\phi_{x_i}/V(x_i)$, for the Stokes Hessian. Left: 2nd batch. Mid: 13th batch. Right: 19th batch. Brightness scale differs between the subfigures. Black stars indicate the sample point locations, $x_i$. Dashed gray ellipses indicate the support ellipsoids, $E_{x_i}$. The large circle is the boundary of the domain $\Omega$. Early batches tend to have lots of ellipsoids near the boundary, as compared to later batches. This is because our greedy ellipsoid packing algorithm tries to pick sample points that are far away from sample points in previously chosen batches.}
	\label{fig:batches_intro}
\end{figure}
